---
title: "BostonHousing"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{BostonHousing}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
Attach libraries:
```{r setup}
library(BonusLab)
library(mlbench)
library(caret)
```

Load and preview the dataset:
```{r}
data(BostonHousing)
dim(BostonHousing)
head(BostonHousing)
```
1. Divide the dataset into training and test set:
```{r}
set.seed(42)
inTrain <- caret::createDataPartition(y = BostonHousing$medv, p = .75,list = FALSE)
                                      

training <- BostonHousing[ inTrain,]
testing <- BostonHousing[-inTrain,]
nrow(training)
nrow(testing)
```
Set up sampling method, 10-fold cross-validation:
```{r}
sampling <- trainControl(method = "cv",p=90)

```
2. Run linear models
Run linear model, all variables:
```{r}
lm_res <- train(medv ~ .,data = training, method = 'lm', trControl = sampling)
lm_res
```
Run linear model with forward selection:
```{r}
grid <- data.frame(c(1:(length(BostonHousing)-1)))
names(grid) <- c("nvmax")
lmsubset_res <- train(medv ~ .,data = training,intercept=TRUE,
               method = 'leapForward',tuneGrid=grid, trControl = sampling)
lmsubset_res
```
3) Evaluate the performance of these models on the training set:
```{r}
lm_vs_lmsubset_training <- resamples(list(lm = lm_res, lm_subset = lmsubset_res))
summary(lm_vs_lmsubset_training)
```
4) Fit a ridge regression model using your ridgereg() function to the training dataset for different
values of λ.

Set parameters for running ridgereg() with caret:
```{r}
#- Start information:
ridgereg <- list(type = "Regression",
                 library = "BonusLab",
                 loop = NULL)

#- Parameters:
prm <- data.frame(parameter = c("lambda"),
                  class = c("numeric"),
                  label = c("lambda"))

ridgereg$parameters <- prm

#- Grid
rrGrid <- function(x, y, len = NULL, search = "grid") {
  if(search == "grid") {
    out <- data.frame(lambda = c(0, 0.1, 0.5, 1,2,5,10,15,20))
  }
}

ridgereg$grid <- rrGrid

#- Fit
rrFit <- function(x, y, wts, param, lev, last, weights, classProbs, ...) {
  formula <- y ~ .
  data <- as.data.frame(cbind(x,y))
  lambda <- param$lambda
  BonusLab::ridgereg(formula, data, lambda)
}

ridgereg$fit <- rrFit

#- Pred
rrPred <- function(modelFit, newdata, preProc = NULL, submodels = NULL) {
  newdata <- as.data.frame(newdata)
  predict(modelFit, newdata)
}

ridgereg$predict <- rrPred


#- Prob
ridgereg$prob <- function(modelFit, newdata, preProc = NULL, submodels = NULL) {
  NULL
}
```
Train model:

```{r}
rr_res <- train(medv ~ ., data = training,
                   method = ridgereg,
                   preProc = c("center", "scale"),
                   tuneLength = 8,
                    #tuneGrid=grid,
                   trControl = sampling)
rr_res

```
Compare the lm subset model with 11 variables to the ridge regression on the 
training set:

```{r}
lmsubset_vs_ridge_training <- resamples(list(lm_subset = lmsubset_res,rr=rr_res))
summary(lmsubset_vs_ridge_training)

```

6. Evaluate the performance of all three models on the test dataset:

